Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2021-09-28 mice_synthesizing/paper.Rmd

\bar{u}_m &= \sum_{l = 1} \frac{u^{(l)}}{m}.
\end{aligned}

>>>>

\bar{u}_m &= \sum_{l = 1} \frac{u^{(l)}}{m}.

\end{aligned}

```{r, message = FALSE, warning = FALSE, cache = TRUE, cache.lazy = FALSE}
plan(multisession) # increase speed through futures

true_model_age <- lm(age ~ wgt + hgt, data) # model 1
true_model_wgt <- lm(wgt ~ age + hgt, data) # model 2
true_model_gen <- MASS::polr(gen ~ age + hc + reg, data, Hess = TRUE) # model 3

coefs_age <- broom::tidy(true_model_age)$estimate # extract coefficients of model 1
coefs_wgt <- broom::tidy(true_model_wgt)$estimate # extract coefficients of model 2
coefs_gen <- broom::tidy(true_model_gen)$estimate # extract coefficients of model 3

nsim <- 1000 # use 1000 iterations

bootstrap_samples <- 
  modelr::bootstrap(data = data, n = nsim) %$% 
  strap %>% 
  map(as_tibble)

post <- make.post(data)
post["bmi"] <- "imp[[j]][, i] <- imp[['wgt']][, i] / (imp[['hgt']][, i] / 100)^2"

synthetic_samples <- 
  bootstrap_samples %>%
  future_map(function(x) {
    x %>% mice(m = 5, 
               maxit = 1,
               method = "cart",
               minbucket = 3,
               cp = 1e-08,
               predictorMatrix = pred,
               post = post,
               where = matrix(TRUE, nrow(data), ncol(data)),
               print = F)
}, .options = furrr_options(seed = as.integer(123)))

true_age <- 
  bootstrap_samples %>%
  map_dfr(~lm(age ~ wgt + hgt, .x) %>%
            broom::tidy(conf.int = TRUE))

true_wgt <-
  bootstrap_samples %>%
  map_dfr(~lm(wgt ~ age + hgt, .x) %>% 
            broom::tidy(conf.int = TRUE))

true_gen <- 
  bootstrap_samples %>%
  map_dfr(~MASS::polr(gen ~ age + hc + reg, .x, Hess = TRUE) %>%
            broom::tidy(conf.int = TRUE))

synthetic_age <- 
  synthetic_samples %>%
  map_dfr(function(x) {
    x %$% 
      lm(age ~ wgt + hgt) %>%
      mice:::pool.syn() %>%
      summary(conf.int = TRUE)
    })

synthetic_wgt <- 
  synthetic_samples %>%
  map_dfr(function(x) {
    x %$%
      lm(wgt ~ age + hgt) %>%
      mice:::pool.syn() %>%
      summary(conf.int = TRUE)
  })

synthetic_gen <- 
  synthetic_samples %>%
  map_dfr(function(x) {
    x %$%
      MASS::polr(gen ~ age + hc + reg, Hess = TRUE) %>%
      mice:::pool.syn() %>%
      summary(conf.int = TRUE)
  })
```

```{r}
true_age %>%
  mutate(truth = rep(coefs_age, nrow(.) / length(coefs_age)),
         covered = conf.low < truth & truth < conf.high) %>%
  group_by(term) %>%
  summarize(estimate = mean(estimate),
            bias = mean(estimate - truth),
            var = mean(std.error^2),
            lower = mean(conf.low),
            upper = mean(conf.high),
            coverage = mean(covered), .groups = "drop") %>%
  kable(digits = 3,
        caption = "Bootstrapped regression estimates (1000 times) for age 
        regressed on weight and height.") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

synthetic_age %>%
  mutate(truth = rep(coefs_age, nrow(.) / length(coefs_age)),
         covered = `2.5 %` < truth & truth < `97.5 %`) %>%
  group_by(term) %>%
  summarize(estimate = mean(estimate),
            bias = mean(estimate - truth),
            var = mean(std.error^2),
            lower = mean(`2.5 %`),
            upper = mean(`97.5 %`),
            coverage = mean(covered), .groups = "drop") %>%
  kable(digits = 3,
        caption = "Synthetic regression estimates after bootstrapping (1000 
        times) and synthesizing for age regressed on weight and height.") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

true_wgt %>%
  mutate(truth = rep(coefs_wgt, nrow(.) / length(coefs_wgt)),
         covered = conf.low < truth & truth < conf.high) %>%
  group_by(term) %>%
  summarize(estimate = mean(estimate),
            bias = mean(estimate - truth),
            var = mean(std.error^2),
            lower = mean(conf.low),
            upper = mean(conf.high),
            coverage = mean(covered), .groups = "drop") %>%
  kable(digits = 3,
        caption = "Bootstrapped regression estimates (1000 times) for weight 
        regressed on age and height.") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

synthetic_wgt %>%
  mutate(truth = rep(coefs_wgt, nrow(.) / length(coefs_wgt)),
         covered = `2.5 %` < truth & truth < `97.5 %`) %>%
  group_by(term) %>%
  summarize(estimate = mean(estimate),
            bias = mean(estimate - truth),
            var = mean(std.error^2),
            lower = mean(`2.5 %`),
            upper = mean(`97.5 %`),
            coverage = mean(covered), .groups = "drop") %>%
  kable(digits = 3,
        caption = "Synthetic regression estimates after bootstrapping (1000 
        times) and synthesizing for weight regressed on age and height.") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

true_gen %>%
  mutate(truth = rep(coefs_gen, nrow(.) / length(coefs_gen)),
         covered = conf.low < truth & truth < conf.high) %>%
  group_by(term) %>%
  summarize(estimate = mean(estimate),
            bias = mean(estimate - truth),
            var = mean(std.error^2),
            lower = mean(conf.low),
            upper = mean(conf.high),
            coverage = mean(covered), .groups = "drop") %>%
  kable(digits = 3,
        caption = "Bootstrapped regression estimates (1000 times) for 
        genital Tanner stage regressed on age, head circumference and 
        region. ") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

synthetic_gen %>%
  mutate(truth = rep(coefs_gen, nrow(.) / length(coefs_gen)),
         covered = `2.5 %` < truth & truth < `97.5 %`) %>%
  group_by(term) %>%
  summarize(estimate = mean(estimate),
            bias = mean(estimate - truth),
            var = mean(std.error^2),
            lower = mean(`2.5 %`),
            upper = mean(`97.5 %`),
            coverage = mean(covered), .groups = "drop") %>%
  kable(digits = 3,
        caption = "Synthetic regression estimates after bootstrapping (1000
        times) and synthesizing for genital Tanner stage regressed on age,
        head circumference and region.") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```
